STAT 405 Project

### 2023-09-21 STAT405Project.qmd
fuck
Formatting
cleaned data
Added plots

---
title: 'STAT 405 Project'
format:
  pdf: default
pdf-engine: pdflatex  # You may need to remove this line
---

@@

Solution:
```{r}

@@

>>>>

---
title: 'STAT 405 Project'
format:
  pdf: default

pdf-engine: pdflatex  # You may need to remove this line
echo: false
---

@@

```{r}
#install.packages("readr")
library(readr)

data_set <- read_csv("Hospital_Inpatient_Discharges__SPARCS_De-Identified___2013.csv",show_col_types = FALSE)

cleaned_data <- na.omit(data_set)

@@

```{r}
y <- cleaned_data$`Total Charges`
```

```{r}
plot(length_of_stay, y,  xlab = "Length of Stay", main = "Price vs Length of Stay", ylab = "Price")

lmfs <- lm(y ~ length_of_stay)
abline(lmfs, col = "RED")
```

```{r}
length_of_stay <- strtoi(cleaned_data$`Length of Stay`)
boxplot(cleaned_data$'Total Costs', 
        main="Box Plot of Total Costs",
        ylab= "Total costs")
```

```{r}
options(repr.plot.width = 100, repr.plot.height = 100)

cleaned_data$`Payment Typology 1` <- as.factor(cleaned_data$`Payment Typology 1`)
payments <- table(cleaned_data$`Payment Typology 1`)
pie(payments, main = "Payment Type Distribution", col=rainbow(length(payments)), labels = NA)
legend("left", legend = levels(cleaned_data$`Payment Typology 1`), fill = rainbow(length(payments)), cex = 0.7)
```

```{r}
admission_freq <- table(cleaned_data$`Type of Admission`)

barplot(admission_freq, xlab = "Type Of Admission", main = "Frequencies for Type of Admission", ylab = "Frequency")
```
```{r}
medianCosts <- tapply(cleaned_data$`Total Costs`, cleaned_data$Race, median)
barplot(medianCosts, main = "Median Cost by Race", xlab = "Race", ylab = "Median Cost", col = "purple", names.arg = sort(names(medianCosts)), ylim = c(0, max(medianCosts) * 1.5))
```
```{r}
ageGroups <- table(cleaned_data$`Age Group`)
barplot(ageGroups, main = "Age Group Distribution", xlab = "Age Group", 
        ylab = "Frequency", col = "green", border = "black", ylim = c(0, 300000)) 
```
